Accurate evaluation of dislocation tractions

### 2021-01-13 src/wip/DanielCelisGarza/Accurate_evaluation_of_dislocation_tractions/paper/main.tex
Added dependency list.

\documentclass[11pt]{iopart}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
% Let us use amsmath.
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax
% Let us use amsmath.
\usepackage{amsmath,isomath,amssymb,bm}
\usepackage[noabbrev]{cleveref}
\usepackage[section]{placeins}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode} % Package for algorithm typesetting (pseudo-code).
\usepackage{lmodern}
\graphicspath{{./images/}}
\input{macros.tex}

@@

    \includegraphics[width=0.8\linewidth]{images/force_calc_linear_rectangle.pdf}

@@

The symmetry of the simple test cases can also influence how solution is as the stress fields exhibit symmetries about the dislocation line. If the dislocation is centered at the center of the element and orthogonal to it then the numerical solution becomes more accurate. However isolated test cases are far from typical simulation scenarios. A single quadrature point is often used to evaluate tractions due to the low computational cost and works well for segments which are not close to the surface. This is therefore the benchmark against which we measure the cost-benefit of implementing and utilising the analytic solutions. It should also be noted that by using a single Gauss point, one can use the same FE mesh as for the Gauss points, simplifying the implementation.
%		
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{images/test_gauss_quad.pdf}
    \caption{Simple test cases for an edge segment and surface element perpendicular (a) and parallel (b). The perpendicular dislocation is centered at the midpoint of the surface element, node $\mathbf{x_1}$ is separated by a perpendicular distance $\mathbf{x_1}^z$ to prevent the dislocation from intersecting the surface. On the right, the parallel dislocation runs along the$x$-axis at half the height of the surface element. The nodes of each dislocation line segment are kept at a perpendicular distance of at least one core radius away from the surface element.}
    \label{f:gauss_quad_test}
\end{figure}

@@

        { \includegraphics[width=0.375\linewidth]{images/fe_numbering.pdf} }

@@

        { \includegraphics[width=0.525\linewidth]{images/surf_node_plane.pdf} }

@@

    \includegraphics[width=\linewidth]{images/lrse_thread_map.pdf}

@@

We also plot the relevant stresses for the arrangement described by \cref{f:gauss_quad_test}(b) in \cref{sf:xzepar,sf:yzepar,sf:zzepar}. It is immediately apparent why gauss quadrature fails so spectacularly in \cref{f:rel_err_par_edge}. At low numbers of quadrature points, it fails to appropriately sample the rapidly changing value of $\tilde{\sigma}_{xz}$ at both ends of the dislocation as seen in \cref{sf:xzepar}, as well as the neighbourhood of the dislocation where $\tilde{\sigma}_{yz}$ changes most raplidly as shown in \cref{sf:yzepar}. Moreover, the further away the quadrature points are from the midpoint of the domain, the lower their relative weighting. So even with a relatively large number of them, there can still be large errors. Which is a particularly egregious problem in \cref{sf:yzepar}, and explains why such a large number of quadrature points is required to accurately compute the integral.
\begin{figure}
    \centering
    \subfloat[\label{sf:xzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzperpEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:yzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzperpEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:zzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/szzperpEdgeFiveb.pdf}}
    }

    \subfloat[\label{sf:xzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/sxzparEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:yzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/syzparEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:zzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{images/szzparEdgeFiveb.pdf}}
    }
    \caption{(a) to (c) show the relevant stress fields from a dislocation in the same configuration that yields the plots found in \cref{f:rel_err_perp_edge} as shown in \cref{f:gauss_quad_test}(a), where the closest node is a dislocation core radius away from the surface, $a = 5b$. (e) to (f) does the same for the configuration that yields \cref{f:rel_err_par_edge} as shown in \cref{f:gauss_quad_test}(b), where the whole dislocation is a core radius away from the surface, $a = 5b$. The white line or dot is the dislocation.}
    \label{f:sigma_edge_test_config}
\end{figure}

@@

\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, the $\textrm{A}$ superscript are the stresses calculated from analytic tractions and the $\textrm{N}$ superscript are those coming from numeric tractions where $Q = 1$ (we use the same nomenclature in \cref{f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}). The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}} = [1 0 0]$. It is clear edge effects play a role in the generated stresses. All three components have notable differences from the infinite-domain solutions resulting from the finite constraints. There is also some artifacting (\cref{sf:syyAeperp,sf:sxyAeperp}) arising from the perturbation needed to avoid the singularity in the analytic traction calculation and error propagation from floating point arithmetic, as mentioned in \cref{s:method}. Of note is the large degree of asymmetry between both lobes of \cref{sf:sxxNeperp}, this is not a simple artifact due to numerical precision but a result of the numerical instability of gauss quadrature. Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components.
% TODO #51 make sure captions are correct and set the axes properly in figs 13-15 and 17
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEperp_leg.pdf}}
    }~
    \subfloat{\includegraphics[height = 0.22\linewidth]{sxxNAEperp_leg.pdf}}

    \subfloat[%$\hat{\sigma}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyNEperp_leg.pdf}}
    }~
    \subfloat{\includegraphics[height = 0.22\linewidth]{syyNAEperp_leg.pdf}}

    \hspace*{0.2cm}\subfloat[%$\hat{\sigma}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyNEperp_leg.pdf}}
    }~
    \hspace*{-0.2cm}\subfloat{
        \includegraphics[height = 0.22\linewidth]{sxyNAEperp_leg.pdf}
    }

@@

Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}. Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions. If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting. They are fundamentally different when calculated with numeric tractions. Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible. Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive. It is as absurd as a ship inverts the Archimidean principle. The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxxNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxxNAEpar_leg.pdf}
    }

    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syyNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{syyNAEpar_leg.pdf}
    }

    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxyNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxyNAEpar_leg.pdf}
    }

@@

Perhaps the most evident deformation resulting from the displacement boundaries can be seen when $\vec{b} = \vec{b}_{\textrm{s}}$ in \cref{f:head_vs_ana_vs_num_screw}, where the lobes of the isolines are highly deformed when compared to the infinite-domain solutions. The familiar lobes look very different, but both analytic and numeric tractions yield fairly similar fields.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxzscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzAscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxzAscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzNscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/sxzNscrew_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxzNAscrew_leg.pdf}
    }

    \subfloat[%$\hat{\sigma}_{yz}$.
        \hspace{-0.8cm}\label{sf:szyscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syzscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yz}$.
        \hspace{-0.8cm}\label{sf:syzAscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syzAscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yz}$.
        \hspace{-0.8cm}\label{sf:syzNscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{images/syzNscrew_leg}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{syzNAscrew_leg.pdf}
    }
    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e. the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom. From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript). The subfigure rows from top to bottom represent $\hat{\sigma}_{xz}$ and $\hat{\sigma}_{yz}$.}
    \label{f:head_vs_ana_vs_num_screw}
\end{figure}

@@

It is also worth looking at the stress fields with a finer lens. \Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e. through the line $x = 50\, b$. \Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$. Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses. In general, the non-singular formulation smoothes out the stress line plots. However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions. Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxxEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_syyEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{images/line_sxyEperp_leg.pdf}}
    }

>>>>

\documentclass[11pt]{iopart}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{booktabs}
% Let us use amsmath.
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax
% Let us use amsmath.
\usepackage{amsmath,isomath,amssymb,bm}
\usepackage[noabbrev]{cleveref}
\usepackage[section]{placeins}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{comment}
\usepackage[sort&compress,numbers]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode} % Package for algorithm typesetting (pseudo-code).
\usepackage{lmodern}
% \usepackage{snapshot}
\graphicspath{{./images/}}
\input{macros.tex}

@@

    \includegraphics[width=0.8\linewidth]{force_calc_linear_rectangle.pdf}

@@

The symmetry of the simple test cases can also influence how solution is as the stress fields exhibit symmetries about the dislocation line. If the dislocation is centered at the center of the element and orthogonal to it then the numerical solution becomes more accurate. However isolated test cases are far from typical simulation scenarios. A single quadrature point is often used to evaluate tractions due to the low computational cost and works well for segments which are not close to the surface. This is therefore the benchmark against which we measure the cost-benefit of implementing and utilising the analytic solutions. It should also be noted that by using a single Gauss point, one can use the same FE mesh as for the Gauss points, simplifying the implementation.
%		
\begin{figure}
    \centering
    \includegraphics[width=0.8\linewidth]{test_gauss_quad.pdf}
    \caption{Simple test cases for an edge segment and surface element perpendicular (a) and parallel (b). The perpendicular dislocation is centered at the midpoint of the surface element, node $\mathbf{x_1}$ is separated by a perpendicular distance $\mathbf{x_1}^z$ to prevent the dislocation from intersecting the surface. On the right, the parallel dislocation runs along the$x$-axis at half the height of the surface element. The nodes of each dislocation line segment are kept at a perpendicular distance of at least one core radius away from the surface element.}
    \label{f:gauss_quad_test}
\end{figure}

@@

        { \includegraphics[width=0.375\linewidth]{fe_numbering.pdf} }

@@

        { \includegraphics[width=0.525\linewidth]{surf_node_plane.pdf} }

@@

    \includegraphics[width=\linewidth]{lrse_thread_map.pdf}

@@

We also plot the relevant stresses for the arrangement described by \cref{f:gauss_quad_test}(b) in \cref{sf:xzepar,sf:yzepar,sf:zzepar}. It is immediately apparent why gauss quadrature fails so spectacularly in \cref{f:rel_err_par_edge}. At low numbers of quadrature points, it fails to appropriately sample the rapidly changing value of $\tilde{\sigma}_{xz}$ at both ends of the dislocation as seen in \cref{sf:xzepar}, as well as the neighbourhood of the dislocation where $\tilde{\sigma}_{yz}$ changes most raplidly as shown in \cref{sf:yzepar}. Moreover, the further away the quadrature points are from the midpoint of the domain, the lower their relative weighting. So even with a relatively large number of them, there can still be large errors. Which is a particularly egregious problem in \cref{sf:yzepar}, and explains why such a large number of quadrature points is required to accurately compute the integral.
\begin{figure}
    \centering
    \subfloat[\label{sf:xzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{sxzperpEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:yzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{syzperpEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:zzeperp}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{szzperpEdgeFiveb.pdf}}
    }

    \subfloat[\label{sf:xzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{sxzparEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:yzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{syzparEdgeFiveb.pdf}}
    }
    ~
    \subfloat[\label{sf:zzepar}]
    {
        {\includegraphics[trim={0.5cm 0cm 0cm 0cm},clip,width=0.3\linewidth]{szzparEdgeFiveb.pdf}}
    }
    \caption{(a) to (c) show the relevant stress fields from a dislocation in the same configuration that yields the plots found in \cref{f:rel_err_perp_edge} as shown in \cref{f:gauss_quad_test}(a), where the closest node is a dislocation core radius away from the surface, $a = 5b$. (e) to (f) does the same for the configuration that yields \cref{f:rel_err_par_edge} as shown in \cref{f:gauss_quad_test}(b), where the whole dislocation is a core radius away from the surface, $a = 5b$. The white line or dot is the dislocation.}
    \label{f:sigma_edge_test_config}
\end{figure}

@@

\Cref{f:head_vs_ana_vs_num_eperp} shows the stress fields corresponding to analytic expressions for image stress components, $\hat{\sigma}_{ij}$ in \cref{eq:imageStressAnalyticEdge1} where no superscript denotes the infinite-domain singular expressions, the $\textrm{A}$ superscript are the stresses calculated from analytic tractions and the $\textrm{N}$ superscript are those coming from numeric tractions where $Q = 1$ (we use the same nomenclature in \cref{f:head_vs_ana_vs_num_epar,f:head_vs_ana_vs_num_screw}). The setup corresponds to the one described in \cref{f:headvstractionfem} where $\vec{b} = \vec{b}_{\textrm{e1}} = [1 0 0]$. It is clear edge effects play a role in the generated stresses. All three components have notable differences from the infinite-domain solutions resulting from the finite constraints. There is also some artifacting (\cref{sf:syyAeperp,sf:sxyAeperp}) arising from the perturbation needed to avoid the singularity in the analytic traction calculation and error propagation from floating point arithmetic, as mentioned in \cref{s:method}. Of note is the large degree of asymmetry between both lobes of \cref{sf:sxxNeperp}, this is not a simple artifact due to numerical precision but a result of the numerical instability of gauss quadrature. Regardless, the overall shape of the isolines is similar in all three solutions for corresponding stress components.
% TODO #51 make sure captions are correct and set the axes properly in figs 13-15 and 17
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxNEperp_leg.pdf}}
    }~
    \subfloat{\includegraphics[height = 0.22\linewidth]{sxxNAEperp_leg.pdf}}

    \subfloat[%$\hat{\sigma}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{syyEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{syyAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{syyNEperp_leg.pdf}}
    }~
    \subfloat{\includegraphics[height = 0.22\linewidth]{syyNAEperp_leg.pdf}}

    \hspace*{0.2cm}\subfloat[%$\hat{\sigma}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyAeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyAEperp_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyNeperp}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyNEperp_leg.pdf}}
    }~
    \hspace*{-0.2cm}\subfloat{
        \includegraphics[height = 0.22\linewidth]{sxyNAEperp_leg.pdf}
    }

@@

Things get markedly more interesting when looking at $\vec{b} = \vec{b}_{\textrm{e2}}$ in \cref{f:head_vs_ana_vs_num_epar}. Of particular note is $\hat{\sigma}_{xx}$, where a comparison between \cref{sf:sxxepar,sf:sxxAepar} and \cref{sf:sxxNepar} reveals one of the major issues with numeric tractions. If we look at the neighbourhood of the dislocation (just to the right), we will find a sign inversion (yellow and green contours as opposed to purple and blue) as well as a drastically different isosurface shape Here the isolines are not merely deformed nor pinched in the way that is indicative of numerical artifacting. They are fundamentally different when calculated with numeric tractions. Image stresses like those can lead dislocations to behave differently than they should, particularly if the sign inversion also comes with an increased force magnitude, which judging from \cref{f:rel_err_par_edge} is quite possible. Specifically, there is a region in the positive $x$-direction away from the dislocation where $\hat{\sigma}_{xx}$ is tensile rather than compressive. It is as absurd as a ship inverts the Archimidean principle. The other two stress fields $\hat{\sigma}_{yy}$, $\hat{\sigma}_{xy}$ follow similar trends to what we have already observed, where the isolines get squashed and flair towards the traction free surface.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xx}$.
        \hspace{-0.8cm}\label{sf:sxxNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxxNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxxNAEpar_leg.pdf}
    }

    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{syyEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{syyAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yy}$.
        \hspace{-0.8cm}\label{sf:syyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{syyNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{syyNAEpar_leg.pdf}
    }

    \hspace*{0.3cm}\subfloat[%$\hat{\sigma}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyAepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyAEpar_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xy}$.
        \hspace{-0.8cm}\label{sf:sxyNepar}]
    {
        {\includegraphics[width=0.25\linewidth]{sxyNEpar_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxyNAEpar_leg.pdf}
    }

@@

Perhaps the most evident deformation resulting from the displacement boundaries can be seen when $\vec{b} = \vec{b}_{\textrm{s}}$ in \cref{f:head_vs_ana_vs_num_screw}, where the lobes of the isolines are highly deformed when compared to the infinite-domain solutions. The familiar lobes look very different, but both analytic and numeric tractions yield fairly similar fields.
\begin{figure}
    \centering
    \subfloat[%$\hat{\sigma}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{sxzscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzAscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{sxzAscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{xz}$.
        \hspace{-0.8cm}\label{sf:sxzNscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{sxzNscrew_leg.pdf}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{sxzNAscrew_leg.pdf}
    }

    \subfloat[%$\hat{\sigma}_{yz}$.
        \hspace{-0.8cm}\label{sf:szyscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{syzscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{A}_{yz}$.
        \hspace{-0.8cm}\label{sf:syzAscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{syzAscrew_leg.pdf}}
    }~
    \subfloat[%$\hat{\sigma}^\textrm{N}_{yz}$.
        \hspace{-0.8cm}\label{sf:syzNscrew}]
    {
        {\includegraphics[width=0.25\linewidth]{syzNscrew_leg}}
    }~
    \subfloat{
        \includegraphics[height = 0.227\linewidth]{syzNAscrew_leg.pdf}
    }
    \caption{Image stresses for a screw dislocation with $\vec{l} = [0 0 1]$, $\vec{b} = [0 0 1]$, where $a = 5~b$, with coordinates $(25.6410,\, 1000)~b$, i.e. the centre of the first FE from the surface at $x=0$, and in the centre of the simulation box from top to bottom. From left to right, the subfigure columns correspond to the stress fields for the infinite-domain solution (no superscript), analytic tractions + FEM (A superscript), and numeric tractions ($Q = 1$) + FEM (N superscript). The subfigure rows from top to bottom represent $\hat{\sigma}_{xz}$ and $\hat{\sigma}_{yz}$.}
    \label{f:head_vs_ana_vs_num_screw}
\end{figure}

@@

It is also worth looking at the stress fields with a finer lens. \Cref{f:line_head_vs_ana_vs_num} shows line plots through the first set of nodes away from the traction surface, i.e. through the line $x = 50\, b$. \Cref{sf:line_sxxperp,sf:line_syyeperp,sf:line_sxyeperp} correspond to to $\vec{b} = \vec{b}_{\textrm{e1}}$, \cref{sf:line_sxxepar,sf:line_syyepar,sf:line_sxyepar} $\vec{b} = \vec{b}_{\textrm{e2}}$ and \cref{sf:line_sxzscrew,sf:line_syzscrew} to $\vec{b} = \vec{b}_{\textrm{s}}$. Here the singular nature of the infinite-domain solutions is evidenced by the sharp spikes in the stresses. In general, the non-singular formulation smoothes out the stress line plots. However, there are a few instances where the numeric tractions lead to larger spikes than even the infinite-domain solutions. Again, the general shape of the line plots is the same but the tendancy for numerical tractions to spike under specific circumstances is evident in almost every case.
\begin{figure}
    \centering
    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxperp}]
    {
        {\includegraphics[width=0.3\linewidth]{line_sxxEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{line_syyEperp_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyeperp}]
    {
        {\includegraphics[width=0.3\linewidth]{line_sxyEperp_leg.pdf}}
    }

    \subfloat[$\hat{\sigma}_{xx}$.\label{sf:line_sxxepar}]
    {
        {\includegraphics[width=0.3\linewidth]{line_sxxEpar_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{yy}$.\label{sf:line_syyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{line_syyEpar_leg.pdf}}
    }~
    \subfloat[$\hat{\sigma}_{xy}$.\label{sf:line_sxyepar}]
    {
        {\includegraphics[width=0.3\linewidth]{line_sxyEpar_leg.pdf}}
    }
